Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-10 VegOzone.tex
Rename and remove figures

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{climatediagram}
  \includegraphics[width=8.3cm]{fig05}
  \caption{Climate diagram following Walter and Lieth. The diagram is based on climatological data for Svanvik/Pasvik (1992--2012). Monthly averaged temperatures (red line) are displayed with standard error of the mean as error band. Averaged monthly accumulated precipitation (blue bars) is shown with a standard deviation of mean as error bars. Months with average temperatures below freezing are denoted with a star.}
  \label{fig:climatediagram}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_spline}
  \includegraphics[width=8.3cm]{fig06}
  \caption{Ozone climatologies. Fennoscandia combines all available data from Jergul/Karasjok, Esrange, and Pallas. The density distributions are shown together with a multi-annual mean of daily \chem{[O_3]} (climatology). Splines have been fitted through daily mean \chem{[O_3]}. The climatology of daily mean ozone is shown together with $1\,\sigma$ standard deviation and standard error of the mean. Since \chem{[O_3]} are strongly correlated for sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN) (see Fig.~\ref{fig:density_distribution}), data of these have been averaged together to derive a climatology for northern Fennoscandia. (a) Northern Fennoscandia; (b) Svanvik.}
  \label{fig:ozone_climatology_fenoscandic_obs_spline}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=12cm]{fig08}
  \caption{2018/19 anomalies of key environmental variables at Svanhovd displayed as percentages of days significantly deviating from climatological mean through standard deviation for each month. Negative deviations from the climatology are shown as a negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates statistical significance under the assumption of a normal distribution ($15.9\,\unit{\%}$, $30.8\,\unit{\%}$ for Precip.). (a) Temperature; (b) precipitation; (c) global irradiance; (d) ozone.}
  \label{fig:anomalies_svanvik}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_grassland}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_grassland}
  \includegraphics[width=8.3cm]{fig07fin}
\caption{Construction of bespoke response functions for grassland. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_grassland}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_func_opt_mean}
  \includegraphics[width=8.3cm]{fig10}
  \caption{Proposed metric to test bespoke response functions. GS (May--August) climatological averages and standard deviation of $g_\mathrm{sto}^k$ (Eq.~(\ref{eq:stomatal})) relative to $g_\mathrm{max}^k$ at noon (averaged over $11\,\unit{am}-1\,\unit{pm}$ local time) and in the morning (averaged over $5-9\,\unit{am}$ local time) are shown for (a) deciduous tree; (b) coniferous tree; (c) perennial grassland. For simplicity, $f_\mathrm{SWP}$ is neglected in this calculation.}
  \label{fig:javis_func_opt_mean}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig11}
  \caption{$\mathrm{DO_3SE}$ modeling $\mathrm{POD_1}$ results for (a) deciduous trees, (b) coniferous trees, and (c) perennial grasslands at Svanhovd in 2018 (pink) and 2019 (purple). The results varied depending on parameterizations of temperature response functions (MM, Cold, and Subarctic, details in Table~\ref{tab:sensitivity_tests_temp}), growing season (MM (squares) or bespoke (circles), details in Table~\ref{tab:sensitivity_tests_gs}), light response functions (first, second and third point attached by a line are depicting the MM, PPFD0.8 and PPFD1.2, details in Table~\ref{tab:sensitivity_tests_light}), and the effect of taking SWP into account (filled symbols without and open symbols with effects of drought kept in the model). Critical levels for ozone damage \citet{ICP:MappingManual2017,ESPR:Hayes2021} are given as dashed horizontal lines. Note that the horizontal axis is only categorical.}
  \label{fig:pody_rel}
\end{figure}

>>>>

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{climatediagram}
  \includegraphics[width=8.3cm]{fig04}
  \caption{Climate diagram following Walter and Lieth. The diagram is based on climatological data for Svanvik/Pasvik (1992--2012). Monthly averaged temperatures (red line) are displayed with standard error of the mean as error band. Averaged monthly accumulated precipitation (blue bars) is shown with a standard deviation of mean as error bars. Months with average temperatures below freezing are denoted with a star.}
  \label{fig:climatediagram}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_spline}
  \includegraphics[width=8.3cm]{fig05}
  \caption{Ozone climatologies. Fennoscandia combines all available data from Jergul/Karasjok, Esrange, and Pallas. The density distributions are shown together with a multi-annual mean of daily \chem{[O_3]} (climatology). Splines have been fitted through daily mean \chem{[O_3]}. The climatology of daily mean ozone is shown together with $1\,\sigma$ standard deviation and standard error of the mean. Since \chem{[O_3]} are strongly correlated for sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN) (see Fig.~\ref{fig:density_distribution}), data of these have been averaged together to derive a climatology for northern Fennoscandia. (a) Northern Fennoscandia; (b) Svanvik.}
  \label{fig:ozone_climatology_fenoscandic_obs_spline}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=12cm]{fig06}
  \caption{2018/19 anomalies of key environmental variables at Svanhovd displayed as percentages of days significantly deviating from climatological mean through standard deviation for each month. Negative deviations from the climatology are shown as a negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates statistical significance under the assumption of a normal distribution ($15.9\,\unit{\%}$, $30.8\,\unit{\%}$ for Precip.). (a) Temperature; (b) precipitation; (c) global irradiance; (d) ozone.}
  \label{fig:anomalies_svanvik}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_grassland}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_grassland}
  \includegraphics[width=8.3cm]{fig07}
\caption{Construction of bespoke response functions for grassland. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_grassland}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_func_opt_mean}
  \includegraphics[width=8.3cm]{fig08}
  \caption{Proposed metric to test bespoke response functions. GS (May--August) climatological averages and standard deviation of $g_\mathrm{sto}^k$ (Eq.~(\ref{eq:stomatal})) relative to $g_\mathrm{max}^k$ at noon (averaged over $11\,\unit{am}-1\,\unit{pm}$ local time) and in the morning (averaged over $5-9\,\unit{am}$ local time) are shown for (a) deciduous trees; (b) coniferous trees; (c) perennial grassland. For $f_\mathrm{SWP}$ is connected to a plant hydraulic model within $\mathrm{DO_3SE}$ it left out in this calculation.}
  \label{fig:javis_func_opt_mean}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig09}
  \caption{$\mathrm{DO_3SE}$ modeling $\mathrm{POD_1}$ results for (a) deciduous trees, (b) coniferous trees, and (c) perennial grasslands at Svanhovd in 2018 (pink) and 2019 (purple). The results varied depending on parameterizations of temperature response functions (MM, Cold, and Subarctic, details in Table~\ref{tab:sensitivity_tests_temp}), growing season (MM (squares) or bespoke (circles), details in Table~\ref{tab:sensitivity_tests_gs}), light response functions (first, second and third point attached by a line are depicting the MM, PPFD0.8 and PPFD1.2, details in Table~\ref{tab:sensitivity_tests_light}), and the effect of taking SWP into account (filled symbols without and open symbols with effects of drought kept in the model). Critical levels for ozone damage \citet{ICP:MappingManual2017,ESPR:Hayes2021} are given as dashed horizontal lines. Note that the horizontal axis is only categorical.}
  \label{fig:pody_rel}
\end{figure}
